Kepler and the Behemoth: Three Mini-Neptunes in a 40 Million Year Old Association

### 2022-05-01 papers/ms.tex
update ms

Here, we expand on our earlier study of a $38^{+7}_{-6}$ Myr old
Neptune-sized planet in the Kepler field (Kepler-1627~Ab;
\citealt{bouma_kep1627_2022}).  This planet's age was derived based on
its host star's membership in the $\delta$\ Lyr\ cluster.  While our
analysis of the cluster focused on the immediate vicinity of
Kepler-1627 in order to have a reasonable scope,  it became clear that
the $\delta$\ Lyr\ cluster seems to also be part of a much larger
group of similarly aged stars.  This group, which is at a distance of
$\sim$330\,pc from the Sun, spans Cepheus to Hercules (galactic
longitudes, $l$, between 40$^\circ$ and 100$^\circ$), at galactic
latitudes between 0$^\circ$ and 20$^\circ$.  We therefore refer to it
as the Cep-Her complex.  It exhibits significant sub-structure over
its $\approx$250 parsec length, and a detailed analysis of its
memberships, kinematics, and possible origin is currently being
prepared as part of the 1\,kpc expansion of the SPYGLASS project
(R.~Kerr et al.\ in prep).

Our focus is on the intersection of the Cep-Her complex with the
Kepler field.  Cross-matching our Cep-Her members against known Kepler
Objects of Interest (KOIs; \citealt{thompson_planetary_2018}) yielded
four candidate cluster members: Kepler-1627, Kepler-1643, KOI-7368,
and KOI-7913.  Given our earlier analysis of Kepler-1627, we focus
here on the latter three objects.  After analyzing the relevant
properties of Cep-Her (Section~\ref{sec:cluster}), we derive the
stellar properties (Section~\ref{sec:stars}) and validate the
planetary nature of each system using a combination of the Kepler
photometry and high-resolution imaging (Section~\ref{sec:planets}).
We conclude with a discussion of mini-Neptune size evolution, and
point out possible directions for future work
(Section~\ref{sec:disc_conc}).

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.99\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
  {\bf Positions and velocities of candidate members of the Cep-Her
  complex.}
  {\it Top row}: On-sky positions in galactic coordinates.  Black
  points are stars for which group membership is more secure than for
  gray points.  Kepler-1627 is in the outskirts of the $\delta$ Lyr
  cluster \citep{bouma_kep1627_2022}, which is centered at $(l,b)
  \approx (66^\circ, 12^\circ)$.
  The Kepler footprint is shown in gray.
  {\it Middle row}: Galactic positions.  The Sun is at $(X, Y, Z) =
  (0, 0, 20.8)$\,pc; lines of constant heliocentric distance are
  shown between 250 and 400\,pc, spaced by 50\,pc.
  {\it Bottom row}: Galactic tangential velocities (left) and
  galactic longitudinal velocity versus galactic longitude (right).
  The gray band in the lower-right shows the $\pm$1-$\sigma$
  projection of the Solar velocity with respect to the local standard
  of rest.  There is a strong spatial and kinematic overlap between
  Kepler-1643 and RSG-5 (magenta).  The local population
  of candidate young stars around KOI-7368 and KOI-7913 is more
  diffuse -- we call this region ``CH-2'' (lime-green).
  The selection method for all of the stars displayed
  is described in Section~\ref{subsec:members}.
	\label{fig:XYZvtang}
	}
\end{figure*}

@@

Our focus is on a region of the Galaxy 200 to 500\,pc
from the Sun, above the galactic plane, and spanning galactic
longitudes of $40^\circ$ to $100^\circ$.  Two rich clusters in
this region are the $\delta$~Lyra cluster
\citep{stephenson_possible_1959} and RSG-5 \citep{roser_nine_2016}.
Each of these clusters was known before Gaia.  Their reported ages are
between 30 and 60\,Myr.  Early empirical evidence that these two
clusters could be part of a large and more diffuse population was
apparent in the Gaia-based photometric analysis of pre-main-sequence
stars by \citet[][see their Figures~11 and~13]{Zari2018}.  Further
kinematic connections and complexity were highlighted by
\citet{KounkelCovey2019}, who included these previously known groups
in the larger structures dubbed ``Theia~73'' and
``Theia~96''\footnote{See their visualization online at
\url{http://mkounkel.com/mw3d/mw2d.html} (accessed 15 March 2022)}.
The connection made by \citet{KounkelCovey2019} between the previously
known open clusters and the other groups in the region was made as
part of an unsupervised clustering analysis of the Gaia DR2 positions
and on-sky velocities with a subsequent manual ``stitching'' step.
Their results support the idea that there is an overdensity of 30 to
60\,Myr old stars in this region of the Galaxy.  \citet{Kerr2021}, in
a volume-limited analysis of the Gaia DR2 point-source catalog out to
one third of a kiloparsec, identified three of the nearest
sub-populations, dubbed ``Cepheus-Cygnus'', ``Lyra'', and
``Cerberus''.  \citet{Kerr2021} reported ages for each of these
subgroups between 30 and 35 Myr.

@@

The possibility that the $\delta$~Lyr cluster, RSG-5, and the
sub-populations identified by \citet{Kerr2021} share a common origin
has yet to be fully substantiated, but preliminary clustering results
from the 1\,kpc SPYGLASS analysis (R.~Kerr et al.\ in prep) suggest
the presence of contiguous stellar populations connecting each of
these groups.  In this work, our primary interest in the region stems
from the fact that a portion of it was observed by Kepler
(Figure~\ref{fig:XYZvtang}, top panel).  To further explore this
sub-population, we select candidate Cep-Her members through four
steps, the first three being identical to those described in Section~3
of \citet{Kerr2021}.  We briefly summarize them here.

@@

The second step is to perform an unsupervised HDBScan clustering on
the photometrically selected population
\citep{campello_hierarchical_2015,mcinnes_hdbscan_2017}.  The
parameters we use in the clustering are $\{ X, Y, Z, c v_b, c v_{l^*}
\} $, where $c$ is the size-velocity corrective factor, which is taken
as $c=6\,{\rm pc / km\,s}^{-1}$ to ensure that the spatial and
velocity scales have identical standard deviations.  Positions are
computed assuming the \texttt{astropy v4.0} coordinate standard
\citep{astropy_2018}, which places the Sun $8122$ pc from the galactic
center, and assumes the solar velocity with respect to the local
standard of rest from \citet{schonrich_local_2010}.  As input
parameters to HDBScan, we set the minimum $\epsilon$ threshold past
which clusters cannot be fragmented as $25$\,pc in physical space, and
$25/c$\,\kms\ in velocity.  The minimum cluster size $N$ is set to 10, as
is $k$, the parameter used to define the ``core distance'' density
metric.

This unsupervised clustering in this case yielded 8 distinct subgroups.
These groups are then used as the ``seed'' populations for the third
step, which is to search for objects at least as close to the 10$^{\rm
th}$ nearest HDBScan-identified member in space-velocity coordinates.
This third step yields stars that are spatially and kinematically
close to the photometrically young stars, but which cannot be
identified as young based on their positions in the color--absolute
magnitude diagram.

The outcome of the analysis up to the point of the third step is shown
in Figure~\ref{fig:XYZvtang}.  To enable a selection cut that filters
out field-star contaminants, we also compute a weight metric,
$D$, defined such that the group member with the smallest core
distance has $D=1$, the group member with the greatest core
distance has $D=0$, and weights for the other group members are
log-normally distributed between these two extremes.  After applying a
set of quality cuts on the astrometry and
photometry,\footnote{$\varpi/\sigma_\varpi>5$; $G/\sigma_{G}>50$;
$G_{\rm RP}/\sigma_{G_{RP}}>20$; $G_{\rm BP}/\sigma_{G_{BP}}>20$.}
this procedure yields $D \sim \log_{10}\mathcal{N}(-1.55,0.61)$.
To visualize the results, in Figure~\ref{fig:XYZvtang} we show
12{,}436 objects with $D>0.02$ as gray points, and 
4{,}763 objects with $D>0.10$ as black points.  The previously
known $\delta$~Lyr\ cluster is visible at $(l,b)=(68^\circ,15^\circ$)
and $(v_{l'}, v_b)=(-4.5 ,-4 )\mkms$.  RSG-5 is visible at
$(l,b)=(83^\circ,6^\circ)$, $(v_{l'}, v_b)=(5.5 ,-3.5 )\mkms$.  Most
of the other subclusters, including in Cep-Cyg
($l,b=90^\circ,7^\circ$) and Cerberus ($l,b=48^\circ,18^\circ$) are
too small or dispersed to have previously been analyzed in great
detail.

%
% KOI match numbers from calc_CepHer_group_numbers.py
%
Our fourth and final step was to cross-match the candidate Cep-Her
member list against all known Kepler Objects of Interest.  We used the
Cumulative KOI table from the NASA Exoplanet Archive from 27 March
2022, and also compared against the \texttt{q1\_q17\_dr25} table
\citep{thompson_planetary_2018}.  From the candidate members with
weights exceeding 0.02, this yielded 11 known false positives, 6
``confirmed'' planets, and 8 ``candidate'' planets.  Inspection of the
Kepler data validation summaries and Robovetter classifications for
these objects showed whether they were potentially consistent with
being {\it i)} planets, and {\it ii)} $\lesssim 10^8$ years old, based
on the presence of rotational modulation at the expected period and
amplitude \citep[{e.g.},][Figure~9]{rebull_rotation_2020}. 
Four
objects passed both cuts: Kepler-1627, Kepler-1643,
KOI-7368, and KOI-7913.

Figure~\ref{fig:XYZvtang} shows the positions of the KOIs along
various projections.  Kepler-1643 is near the core RSG-5 population
both spatially and kinematically.  KOI-7368 and KOI-7913 are in a
diffuse region $\approx$40\,pc above RSG-5 in $Z$ and $\approx$100\,pc
closer to the Sun in $Y$.  In tangential galactic velocity space,
there is some kinematic overlap between the region the latter two KOIs
are in and the main RSG-5 group.

%
% Numbers are from RSG-5_auto_XYZ_vl_vb_cut.csv,
% CH-2_auto_XYZ_vl_vb_cut.csv
%
We define two sets of stars in the local vicinity of our objects of
interest.  For candidate RSG-5 members, we require:
\begin{align}
  X/{\rm pc} &\in [45, 75] \nonumber \\
  Y/{\rm pc} &\in [320, 350] \nonumber \\
  Z/{\rm pc} &\in [40, 80] \nonumber \\
  v_b/{\rm km\,s^{-1}} &\in [-4, -2.5] \nonumber \\
  v_{l^*}/{\rm km\,s^{-1}} &\in [3.5, 6], \nonumber
\end{align}
though the cluster does have a greater spatial extent toward smaller
$X$ (Figure~\ref{fig:XYZvtang}, middle panels).  For the diffuse stars
near KOI-7368 and KOI-7913, we require
\begin{align}
  X/{\rm pc} &\in [20, 70] \nonumber \\
  Y/{\rm pc} &\in [230, 270] \nonumber \\
  Z/{\rm pc} &\in [75, 105] \nonumber \\
  v_b/{\rm km\,s^{-1}} &\in [-3.5, -1.5] \nonumber \\
  v_{l^*}/{\rm km\,s^{-1}} &\in [2, 6] \nonumber
\end{align}
and we call this latter set of stars ``CH-2'', using the preliminary 
Cep-Her (CH) subgroup identifier from R.~Kerr et al.\ (in prep).
These cuts yield
\nrsgfive\ candidate RSG-5 members, and \nchtwo\ candidate CH-2
members.  These stars are listed in Appendix~\ref{app:members}, as are
the Cep-Her candidates that were observed by Kepler, and all of our
candidate matches against the Kepler Objects of Interest.  An important
consideration, especially for CH-2, is the contamination rate by field
stars.  We assess this in the following section.

@@

Figure~\ref{fig:age} also shows that most RSG-5 and CH-2 members
overlap with the $\delta$~Lyr cluster, and that the groups are
therefore roughly the same age.  To quantify this, we use the method
introduced by \citet[][their Section~6.3]{gagne_mutau_2020}.  The idea
is to fit the pre-main-sequence loci of a set of reference clusters,
and to then model the locus of the target cluster as a linear
combination of these reference cluster loci.  For our reference
clusters, we used UCL, IC\,2602, and the Pleiades, with the
memberships reported by \citet{Damiani2019} and
\cite{CantatGaudin2018a} respectively.  We adopted ages of 16\,Myr for
UCL \citep{pecaut_star_2016}, 38\,Myr for IC\,2602
\citep{david_ages_2015,randich_gaiaeso_2018} and 112\,Myr for the
Pleiades \citep{dahm_2015}.  These assumptions and the subsequent
processing steps taken to exclude field stars and binaries were
identical to those described in \citet{bouma_kep1627_2022}.  The mean
and uncertainty of the resulting age posterior are $46^{+9}_{-7}$\,Myr
for RSG-5, and $36^{+10}_{-8}$\,Myr for CH-2.  For comparison, this
procedure yields an age for the $\delta$~Lyr cluster of
$38^{+6}_{-5}$\,Myr.  The older isochronal age of RSG-5 is consistent
with its location relative to the $\delta$~Lyr cluster in the upper
left panel of Figure~\ref{fig:age}.

@@

For CH-2, 13/19 stars have rotation periods that are obviously faster
than their counterparts in the Pleiades (68\%).  4 stars, not included
in the preceding numerator, are M-dwarfs with rotation periods between
10 and 12.5 days.  As just discussed, the age interpretation for these
M-dwarfs is not obvious.  Regardless, the $\approx$15\% false positive
rate for CH-2 determined from the CAMD seems consistent with our
fraction of detected rotation periods; RSG-5 was missing rotation
periods for $\approx$15\% of its candidate members, even though all of
its stars appear photometrically consistent with being on a single
pre-main-sequence locus.

@@

We have shown that Kepler-1643~b, KOI-7368~b, and KOI-7913~Ab are 40
to 50 million years old, and that each system is most likely
planetary.  The evidence for the planetary interpretation comes from
an application of \texttt{VESPA} to the Kepler data, alongside new
imaging from NIRC2.  The validity of the \texttt{VESPA} framework
rests on the premise that non-astrophysical false positives can be
rejected.  
This seems to be the case for all three objects, even though
Kepler-1643 and KOI-7368 
both show weak centroid offsets between the in
and out-of-transit phases.  For both cases, the weak observed shifts
are consistent with being caused by starspot-induced variability in
specific quarters spuriously moving the stellar center-of-light.
Independently, our imaging rules out companion stars with the
brightness and positions that would be needed to otherwise explain the
reported shifts.  All three objects are therefore validated planets.

>>>>

Here, we expand on our earlier study of a $38^{+7}_{-6}$ Myr old
Neptune-sized planet in the Kepler field (Kepler-1627~Ab;
\citealt{bouma_kep1627_2022}).  This planet's age was derived based on
its host star's membership in the $\delta$\ Lyr\ cluster.  While our
analysis of the cluster focused on the immediate vicinity of
Kepler-1627 in order to have a reasonable scope,  it became clear that
the $\delta$\ Lyr\ cluster seems to also be part of a much larger
group of similarly aged stars.  This association, which is at an
average distance of 330\,pc from the Sun, spans Cepheus to Hercules
(galactic longitudes, $l$, between 40$^\circ$ and 100$^\circ$), at
galactic latitudes between 0$^\circ$ and 20$^\circ$.  An assessment of
its membership, substructure, and age distribution will be provided as
part of the 1\,kpc expansion of the SPYGLASS project (R. Kerr et al.\
in prep), where it is given the name Cep-Her, after the endpoint
constellations.

Our focus is on the intersection of the Cep-Her complex with the
Kepler field.  Cross-matching the stars thought to be in Cep-Her against known Kepler
Objects of Interest (KOIs; \citealt{thompson_planetary_2018}) yielded
four candidate cluster members: Kepler-1627, Kepler-1643, KOI-7368,
and KOI-7913.  Given our earlier analysis of Kepler-1627, we focus
here on the latter three objects.  After analyzing the relevant
properties of Cep-Her (Section~\ref{sec:cluster}), we derive the
stellar properties (Section~\ref{sec:stars}) and validate the
planetary nature of each system using a combination of the Kepler
photometry and high-resolution imaging (Section~\ref{sec:planets}).
We conclude with a discussion of mini-Neptune size evolution, and
point out possible directions for future work
(Section~\ref{sec:disc_conc}).

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.99\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
  {\bf Positions and velocities of candidate members of the Cep-Her
  complex.}
  {\it Top row}: On-sky positions in galactic coordinates.  Black
  points are stars for which group membership is more secure than for
  gray points.  Kepler-1627 is in the outskirts of the $\delta$\ Lyr
  cluster \citep{bouma_kep1627_2022}, which is centered at $(l,b)
  \approx (66^\circ, 12^\circ)$.
  The Kepler footprint is shown in gray.
  {\it Middle row}: Galactic positions.  The Sun is at $(X, Y, Z) =
  (0, 0, 20.8)$\,pc; lines of constant heliocentric distance are
  shown between 250 and 400\,pc, spaced by 50\,pc.
  {\it Bottom row}: Galactic tangential velocities (left) and
  galactic longitudinal velocity versus galactic longitude (right).
  The gray band in the lower-right shows the $\pm$1-$\sigma$
  projection of the Solar velocity with respect to the local standard
  of rest \citep{schonrich_local_2010}.  There is a strong spatial and kinematic overlap between
  Kepler-1643 and RSG-5 (magenta).  The local population
  of candidate young stars around KOI-7368 and KOI-7913 is more
  diffuse -- we call this region ``CH-2'' (lime-green).
  The selection method for all of the stars displayed
  is described in Section~\ref{subsec:members}.
	\label{fig:XYZvtang}
	}
\end{figure*}

@@

Our focus is on a region of the Galaxy 200 to 500\,pc
from the Sun, above the galactic plane, and spanning galactic
longitudes of $40^\circ$ to $100^\circ$.  Two rich clusters in
this region are the $\delta$\ Lyr cluster
\citep{stephenson_possible_1959} and RSG-5 \citep{roser_nine_2016}.
Each of these clusters was known before Gaia.  Their reported ages are
between 30 and 60\,Myr.  Early empirical evidence that these two
clusters could be part of a large and more diffuse population was
apparent in the Gaia-based photometric analysis of pre-main-sequence
stars by \citet[][see their Figures~11 and~13]{Zari2018}.  Further
kinematic connections and complexity were highlighted by
\citet{KounkelCovey2019}, who included these previously known groups
in the larger structures dubbed ``Theia~73'' and
``Theia~96''\footnote{See their visualization online at
\url{http://mkounkel.com/mw3d/mw2d.html} (accessed 15 March 2022)}.
The connection made by \citet{KounkelCovey2019} between the previously
known open clusters and the other groups in the region was made as
part of an unsupervised clustering analysis of the Gaia DR2 positions
and on-sky velocities with a subsequent manual ``stitching'' step.
Their results support the idea that there is an overdensity of 30 to
60\,Myr old stars in this region of the Galaxy.  \citet{Kerr2021}, in
a volume-limited analysis of the Gaia DR2 point-source catalog out to
one third of a kiloparsec, identified three of the nearest
sub-populations, dubbed ``Cepheus-Cygnus'', ``Lyra'', and
``Cerberus''.  \citet{Kerr2021} reported ages for each of these
subgroups between 30 and 35 Myr.

@@

The possibility that the $\delta$~Lyr cluster, RSG-5, and the
sub-populations identified by \citet{Kerr2021} share a common origin
has yet to be fully substantiated, but preliminary clustering results
from the 1\,kpc SPYGLASS analysis (R.~Kerr et al.\ in prep) suggest
the presence of contiguous stellar populations connecting each of
these groups in space-velocity coordinates.  
In other words, the stars appear to be co-moving, though with a
continuous gradient in velocity as a function of position
(Figure~\ref{fig:XYZvtang}, lower panels).
In this work, our primary interest in the region stems
from the fact that a portion of it was observed by Kepler
(Figure~\ref{fig:XYZvtang}, top panel).  To further explore this
sub-population, we select candidate Cep-Her members through four
steps, the first three being identical to those described in Section~3
of \citet{Kerr2021}.  We briefly summarize them here.

@@

The second step is to perform an unsupervised HDBSCAN clustering on
the photometrically selected population
\citep{campello_hierarchical_2015,mcinnes_hdbscan_2017}.  The
parameters we use in the clustering are $\{ X, Y, Z, c v_b, c v_{l^*}
\} $, where $c$ is the size-velocity corrective factor, which is taken
as $c=6\,{\rm pc / km\,s}^{-1}$ to ensure that the spatial and
velocity scales have identical standard deviations.  Positions are
computed assuming the \texttt{astropy v4.0} coordinate standard
\citep{astropy_2018}. %, which places the Sun $8122$ pc from the galactic
%center, and assumes the solar velocity with respect to the local
%standard of rest from \citet{schonrich_local_2010}.  
As input
parameters to HDBSCAN, we set the minimum $\epsilon$ threshold past
which clusters cannot be fragmented as $25$\,pc in physical space, and
$25/c$\,\kms\ in velocity.  The minimum cluster size $N$ is set to 10, as
is $k$, the parameter used to define the ``core distance'' density
metric.

The unsupervised clustering in this case yielded 8 distinct subgroups.
These groups are then used as the ``seed'' populations for the third
step, which is to search for objects at least as close to the 10$^{\rm
th}$ nearest HDBSCAN-identified member in space-velocity coordinates.
This third step yields stars that are spatially and kinematically
close to the photometrically young stars, but which cannot be
identified as young based on their positions in the color--absolute
magnitude diagram.

The outcome of the analysis up to the point of the third step is shown
in Figure~\ref{fig:XYZvtang}.  To enable a selection cut that filters
out field-star contaminants, we also compute a weight metric,
$D$, defined such that the group member with the smallest core
distance has $D=1$, the group member with the greatest core
distance has $D=0$, and weights for the other group members are
log-normally distributed between these two extremes.  After applying a
set of quality cuts on the astrometry and
photometry\footnote{$\varpi/\sigma_\varpi>5$; $G/\sigma_{G}>50$;
$G_{\rm RP}/\sigma_{G_{RP}}>20$; $G_{\rm BP}/\sigma_{G_{BP}}>20$}
this procedure yields $D \sim \log_{10}\mathcal{N}(-1.55,0.61)$.
To visualize the results, in Figure~\ref{fig:XYZvtang} we show
12{,}436 objects with $D>0.02$ as gray points, and 
4{,}763 objects with $D>0.10$ as black points.  The 
$\delta$~Lyr\ cluster is visible at $(l,b)=(68^\circ,15^\circ$)
and $(v_{l'}, v_b)=(-4.5 ,-4 )\mkms$.  RSG-5 is visible at
$(l,b)=(83^\circ,6^\circ)$, $(v_{l'}, v_b)=(5.5 ,-3.5 )\mkms$.  Most
of the other subclusters, including in Cep-Cyg
($l,b=90^\circ,7^\circ$) and Cerberus ($l,b=48^\circ,18^\circ$) are
too small or dispersed to have previously been analyzed in great
detail.

%
% KOI match numbers from calc_CepHer_group_numbers.py
%
Our fourth and final step was to cross-match the candidate Cep-Her
member list against all known Kepler Objects of Interest.  We used the
Cumulative KOI table from the NASA Exoplanet Archive from 27 March
2022, and also compared against the \texttt{q1\_q17\_dr25} table
\citep{thompson_planetary_2018}.  From the candidate members with
weights exceeding 0.02, this yielded 11 known false positives, 6
confirmed planets, and 8 candidate planets (see Appendix~\ref{app:members}).
To determine whether these objects were
potentially consistent with being {\it i)} planets, and {\it ii)}
$\lesssim 10^8$ years old, we inspected the Kepler data validation
reports and Robovetter classifications.  Youth was assessed based on
the presence of rotational modulation at the expected period and
amplitude \citep[{e.g.},][]{rebull_rotation_2020}. 
Planetary status was assessed through the Robovetter flags, and by
requiring non-grazing transits with ${\rm S/N}>10$.
Four objects passed both cuts: Kepler-1627, Kepler-1643, KOI-7368, and
KOI-7913.
% FIXME: if you need to add lines, "One object (Kepler-1933) was ambiguous,

Figure~\ref{fig:XYZvtang} shows the positions of these KOIs along
various projections.  Kepler-1643 is near the core RSG-5 population
both spatially and kinematically.  KOI-7368 and KOI-7913 are in a
diffuse region $\approx$40\,pc above RSG-5 in $Z$ and $\approx$100\,pc
closer to the Sun in $Y$.  In tangential galactic velocity space,
there is some kinematic overlap between the region containing the latter two KOIs
and the main RSG-5 group.

%
% Numbers are from RSG-5_auto_XYZ_vl_vb_cut.csv,
% CH-2_auto_XYZ_vl_vb_cut.csv
%
We define two sets of stars in the local vicinity of our objects of
interest.  For candidate RSG-5 members near Kepler-1643, we require:
\begin{align}
  X/{\rm pc} &\in [45, 75] \nonumber \\
  Y/{\rm pc} &\in [320, 350] \nonumber \\
  Z/{\rm pc} &\in [40, 80] \nonumber \\
  v_b/{\rm km\,s^{-1}} &\in [-4, -2.5] \nonumber \\
  v_{l^*}/{\rm km\,s^{-1}} &\in [3.5, 6], \nonumber
\end{align}
though RSG-5 does have a greater spatial extent toward smaller
$X$ (Figure~\ref{fig:XYZvtang}, middle panels).  For the diffuse stars
near KOI-7368 and KOI-7913, we require
\begin{align}
  X/{\rm pc} &\in [20, 70] \nonumber \\
  Y/{\rm pc} &\in [230, 270] \nonumber \\
  Z/{\rm pc} &\in [75, 105] \nonumber \\
  v_b/{\rm km\,s^{-1}} &\in [-3.5, -1.5] \nonumber \\
  v_{l^*}/{\rm km\,s^{-1}} &\in [2, 6] \nonumber
\end{align}
and we call this latter set of stars ``CH-2'', using the preliminary 
Cep-Her (CH) subgroup identifier from R.~Kerr et al.\ (in prep).
These cuts yielded
\nrsgfive\ candidate RSG-5 members, and \nchtwo\ candidate CH-2
members.  These stars are listed in Appendix~\ref{app:members}, as are
the Cep-Her candidates that were observed by Kepler. 
%An important
%consideration, especially for CH-2, is the contamination rate by field
%stars.  We assess this in the following section.

@@

Figure~\ref{fig:age} also shows that most RSG-5 and CH-2 members
overlap with the $\delta$~Lyr cluster, and that the groups are
therefore roughly the same age.  To quantify this, we use the method
introduced by \citet[][their Section~6.3]{gagne_mutau_2020}.  The idea
is to fit the pre-main-sequence loci of a set of reference clusters,
and to then model the locus of the target cluster as a linear
combination of these reference cluster loci.  For our reference
clusters, we used UCL, IC\,2602, and the Pleiades, with the
memberships reported by \citet{Damiani2019} and
\cite{CantatGaudin2018a} respectively.  We adopted ages of 16\,Myr for
UCL \citep{pecaut_star_2016}, 38\,Myr for IC\,2602
\citep{david_ages_2015,randich_gaiaeso_2018} and 112\,Myr for the
Pleiades \citep{dahm_2015}.  These assumptions and the subsequent
processing steps taken to exclude field stars and binaries were
identical to those described in \citet{bouma_kep1627_2022}.  The mean
and uncertainty of the resulting age posterior are $46^{+9}_{-7}$\,Myr
for RSG-5, and $36^{+10}_{-8}$\,Myr for CH-2.  For comparison, this
procedure yields an age for the $\delta$~Lyr cluster of
$38^{+6}_{-5}$\,Myr.  The older isochronal age of RSG-5 is consistent
with its location relative to the $\delta$~Lyr cluster in the upper
left panel of Figure~\ref{fig:age}.
Generally speaking, this method is expected to be accurate provided
that the metallicities of IC\,2602 and the Cep-Her groups (RSG-5,
CH-2, and the $\delta$~Lyr cluster) are roughly identical.  The
spectroscopic metallicities that we find in Section~\ref{sec:stars}
suggest that this is indeed the case.

@@

For CH-2, 13/19 stars have rotation periods that are obviously faster
than their counterparts in the Pleiades (68\%).  4 stars, not included
in the preceding numerator, are M-dwarfs with rotation periods between
10 and 12.5 days.  As previously noted, the age interpretation for these
M-dwarfs is not obvious.  Regardless, the $\approx$15\% false positive
rate for CH-2 determined from the CAMD seems consistent with our
fraction of detected rotation periods; RSG-5 was missing rotation
periods for $\approx$15\% of its candidate members, even though all of
its stars appear photometrically consistent with being on a single
pre-main-sequence locus.

@@

We have shown that Kepler-1643~b, KOI-7368~b, and KOI-7913~Ab are 40
to 50 million years old, and that each system is most likely
planetary.  The evidence for the planetary interpretation comes from
an application of \texttt{VESPA} to the Kepler data, alongside new
imaging from NIRC2.  The validity of the \texttt{VESPA} framework
rests on the premise that non-astrophysical false positives can be
rejected.  
This seems to be the case for all three objects, even though
Kepler-1643 and KOI-7368 
both show weak centroid offsets between the in
and out-of-transit phases.  For both cases, the observed shifts
are consistent with being caused by starspot-induced variability in
specific quarters spuriously moving the stellar center-of-light.
Independently, our imaging rules out companion stars with the
brightnesses and positions that would be needed to explain the
reported shifts.  All three objects are therefore most likely planets.
